Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-16 code/data-preparation.Rmd
changed code to work with the zip files of the data

```{r}
library(cowplot)
library(dplyr)
library(forcats)
library(ggplot2)
library(randomForest)
library(stringr)
library(tidyr)
library(zip)
```

@@

Load the raw version of the Hamby 172 and 252 bullet comparison data:

```{r}
bullet_train_raw = read.csv("../data/raw/hamby-comparisons.csv")
```

@@

Load in the raw Hamby 224 datasets (sets 1 and 11):

```{r}
hamby224_set1 <- readRDS("../data/raw/h224-set1-features.rds")
hamby224_set11 <- readRDS("../data/raw/h224-set11-features.rds")
```

@@

The following code trims the data provided by Heike of two matching bullet-land signatures

Import the data:

```{r}
signatures <- readRDS("../data/raw/signatures.rds")
```

>>>>

```{r}
library(cowplot)
library(dplyr)
library(forcats)
library(ggplot2)
library(randomForest)
library(readr)
library(stringr)
library(tidyr)
library(zip)
```

@@

Load the raw version of the Hamby 172 and 252 bullet comparison data (provided by Heike and CSAFE):

```{r}
bullet_train_raw = read_csv("../data/raw/hamby-comparisons.csv.zip")
```

@@

Load in the raw Hamby 224 datasets (sets 1 and 11; provided by Heike and CSAFE):

```{r}
if (!file.exists("../data/raw/h224-set1-features.rds")) unzip("../data/raw/h224-set1-features.rds.zip")
if (!file.exists("../data/raw/h224-set11-features.rds")) unzip("../data/raw/h224-set11-features.rds.zip")

hamby224_set1 <- readRDS("../data/raw/h224-set1-features.rds")
hamby224_set11 <- readRDS("../data/raw/h224-set11-features.rds")
```

@@

The following code trims the data provided by Heike of two matching bullet-land signatures.

Import the data (provided by Heike and CSAFE):

```{r}
if (!file.exists("../data/raw/signatures.rds")) unzip("../data/raw/signatures.rds.zip")
signatures <- readRDS("../data/raw/signatures.rds")
```
